Photovoltaic System Reconfiguration strategy foer mismatch condition\\ {\footnotesize \textsuperscript{}}

### 2018-08-20 main.tex
add figure
add fig 2

\section{Assumption of a PV array} \label{assum}
In this paper, we using following definitions of PV arrays, modules, strings and panels. A PV array formed by several parallel connected PV strings, and string is several series connected PV panels. For a PV panel, formed by two or three PV modules connected in series with bypass diodes. An equivalent connection as showed in Fig. \ref{fig1}.
\begin{figure}[htbp]
\centerline{\includegraphics{fig2.png}}
\caption{Definition of PV array and internal components.}
\label{fig1}
\end{figure}

The algorithm we proposed based on following assumptions.

\begin{itemize}
\item The current versus voltage (\textit{I-V}) curve of each panel calculated by algorithm presented in \cite{b6}. This algorithm will analyzes panel's \textit{I-V} curve sample and coordinate to maximum or minimum power point in \textit{P-V} curve.
\item All the panels in PV array have same number (\textit{N}) of modules. For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify MPP voltage and current by index \textit{n}. Those parameter can be directly estimated by the prosess provided in\cite{b7}.
\end{itemize}

Furthermore, it is also assumed that for each string it has same number of panels in PV array. Means every string in PV array have same length. String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.
\begin{figure}[htbp]
\centerline{\includegraphics{fig2.png}}
\caption{Flowchart of reconfiguration algorithm.}
\label{fig2}
\end{figure}

@@

After this procedures is conducted for PV array, all panels will be organized into many groups that from un-shadowed or uniform shadow to fully shadowed group. However, if just simply grouping panels by shadow distribution conditions it may cause electrical connection overhead or unable calculate optimal configuration. To further reconfigure PV system into a better configuration, the replacement part of algorithm will proceed as follow:
\begin{itemize}
\item Sorting group by different shadow distribution conditions, select panels from first group into a PV string which working on high current level.
\item If selected panels' working modules ( \textit{$Q_{M_n}^{*}$} ) less than \textit{$Q_{M_n}$} , select panels from next irradiance level group.
\item If selected panels' \textit{$Q_{M_n}^{*}$} more than \textit{$Q_{M_n}$}, re-select panels to adjust \textit{$Q_{M_n}^{*}$} equal to \textit{$Q_{M_n}$} if it is possible. 
\end{itemize}

\begin{figure}[htbp]
\centerline{\includegraphics{fig2.png}}
\caption{An example of un-uniform shadowed PV array.}
\label{fig3}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics{fig2.png}}
\caption{Organized PV array after first part of Algorithm.}
\label{fig4}
\end{figure}

@@

\section{evaluation of optimization algorithm}
%\subsection{Verification of the Proposed algorithm}
This section verifies the effectiveness of proposed algorithm using LTspice simulation. With pilot example presented in last section, shading scenario as showed in Fig.\ref{fig5a}. To minimize power loss, the proposed algorithm, as described, is applied to reconfigure the system. The resulting configuration is depicted in Fig.\ref{fig5b} and Fig.\ref{fig5c}. 
\begin{figure}[H]
\centering

\subfloat[]{
	\label{fig5a}
	\includegraphics{fig2.png} }

\subfloat[]{
	\label{fig5b}
	\includegraphics{fig2.png} }

\subfloat[]{
	\label{fig5c}
	\includegraphics{fig2.png}}

\caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfigurationfor MPP candidate \{2, 2, 3\} and (c) MPP candidate \{2, 2, 2\}} 
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics{fig2.png}}
\caption{The \textit{P-V} curves for the PV system under first shading scenario before and after reconfiguration.}
\label{fig6}
\end{figure}
The computational time required to find the best configuration in the proposed and existed method is also compared and summarized in Table \ref{tab3}. As shown in Table \ref{tab3}, proposed algorithm achieved high accuracy and less computing time compare with exhaustive search algorithm and methods described in \cite{b10} \cite{b11} \cite{b12}.

>>>>

\section{Assumption of a PV array} \label{assum}
In this paper, we using following definitions of PV arrays, modules, strings and panels. A PV array formed by several parallel connected PV strings, and string is several series connected PV panels. For a PV panel, formed by two or three PV modules connected in series with bypass diodes. An equivalent connection as showed in Fig. \ref{fig1}.
\begin{figure}[htbp]
\centerline{\includegraphics[width=7.2cm]{paper-fig1.png}}
\caption{Definition of PV array and internal components.}
\label{fig1}
\end{figure}

The algorithm we proposed based on following assumptions.
\begin{itemize}
\item The current versus voltage (\textit{I-V}) curve of each panel calculated by algorithm presented in \cite{b6}. This algorithm will analyzes panel's \textit{I-V} curve sample and coordinate to maximum or minimum power point in \textit{P-V} curve.
\item All the panels in PV array have same number (\textit{N}) of modules. For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify MPP voltage and current by index \textit{n}. Those parameter can be directly estimated by the prosess provided in\cite{b7}.
\end{itemize}

Furthermore, it is also assumed that for each string it has same number of panels in PV array. Means every string in PV array have same length. String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.
\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{paper-fig2.png}}
\caption{Flowchart of reconfiguration algorithm.}
\label{fig2}
\end{figure}

@@

After this procedures is conducted for PV array, all panels will be organized into many groups that from un-shadowed or uniform shadow to fully shadowed group. However, if just simply grouping panels by shadow distribution conditions it may cause electrical connection overhead or unable calculate optimal configuration. To further reconfigure PV system into a better configuration, the replacement part of algorithm will proceed as follow:
\begin{itemize}
\item Sorting group by different shadow distribution conditions, select panels from first group into a PV string which working on high current level.
\item If selected panels' working modules ( \textit{$Q_{M_n}^{*}$} ) less than \textit{$Q_{M_n}$} , select panels from next irradiance level group.
\item If selected panels' \textit{$Q_{M_n}^{*}$} more than \textit{$Q_{M_n}$}, re-select panels to adjust \textit{$Q_{M_n}^{*}$} equal to \textit{$Q_{M_n}$} if it is possible. 
\end{itemize}
\begin{figure}[htbp]
\centerline{\includegraphics[width=6.2cm]{paper-fig3.png}}
\caption{An example of un-uniform shadowed PV array.}
\label{fig3}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{paper-fig4.png}}
\caption{Organized PV array after first part of Algorithm.}
\label{fig4}
\end{figure}

@@

\section{evaluation of optimization algorithm}
%\subsection{Verification of the Proposed algorithm}
This section verifies the effectiveness of proposed algorithm using LTspice simulation. With pilot example presented in last section, shading scenario as showed in Fig.\ref{fig5a}. To minimize power loss, the proposed algorithm, as described, is applied to reconfigure the system. The resulting configuration is depicted in Fig.\ref{fig5b} and Fig.\ref{fig5c}. 
\begin{figure}
\centering

\subfloat[]{
	\label{fig5a}
	\includegraphics[width=5cm]{paper-fig5(a).png} }

\subfloat[]{
	\label{fig5b}
	\includegraphics[width=5cm]{paper-fig5(b).png} }

\subfloat[]{
	\label{fig5c}
	\includegraphics[width=5cm]{paper-fig5(c).png}}

\caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfiguration for MPP candidate \{2, 2, 3\} and (c) MPP candidate \{2, 2, 2\}} 
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=6.2cm]{fig2.png}}
\caption{The \textit{P-V} curves for the PV system under first shading scenario before and after reconfiguration.}
\label{fig6}
\end{figure}
The computational time required to find the best configuration in the proposed and existed method is also compared and summarized in Table \ref{tab3}. As shown in Table \ref{tab3}, proposed algorithm achieved high accuracy and less computing time compare with exhaustive search algorithm and methods described in \cite{b10} \cite{b11} \cite{b12}.
